\begin{thebibliography}{50}
\bibitem{Ref:ALICE-detectors}
ALICE Collaboration, ``The experiment", \href{https://alice.cern/experiment}{https://alice.cern/experiment}
\bibitem{Ref:ALICE-detectors-ITS}
ALICE Collaboration, ``Inner Tracking System (ITS2)", \href{https://alice.cern/inner-tracking-system-its-2}{https://alice.cern/inner-tracking-system-its-2}
\bibitem{Ref:ALICE-detectors-TPC}
ALICE Collaboration, ``Time Projection Chamber", \href{https://alice.cern/time-projection-chamber}{https://alice.cern/time-projection-chamber}
\bibitem{Ref:ALICE-detectors-TRD}
ALICE Collaboration, ``Transition Radiation Detector",\href{https://alice.cern/transition-radiation-detector}{https://alice.cern/transition-radiation-detector}
\bibitem{Ref:ALICE-detectors-TOF}
ALICE Collaboration, ``Time of Flight", \href{https://alice.cern/time-flight}{https://alice.cern/time-flight}
\bibitem{Ref:ALICE-detectors-EMCal}
ALICE Collaboration, ``Electromagnetic Calorimeter", \href{https://alice.cern/electromagnetic-calorimeter}{https://alice.cern/electromagnetic-calorimeter}
\bibitem{Ref:ALICE-detectors-PHOS}
ALICE Collaboration, ``Photon Specrometer",\href{https://alice.cern/photon-spectrometer}{https://alice.cern/photon-spectrometer}
\bibitem{Ref:ALICE-detectors-HMPID}
ALICE Collaboration, ``High Momentum Particle Identification Detector", \href{https://alice.cern/high-momentum-particle-identification-detector}{https://alice.cern/high-momentum-particle-identification-detector}
\bibitem{Ref:ALICE-detectors-FIT}
ALICE Collaboration, ``Fast Interaction Trigger", \href{https://alice.cern/fast-interaction-trigger}{https://alice.cern/fast-interaction-trigger}
\bibitem{Ref:ALICE-detectors-MFT}
ALICE Collaboration, ``Muon forward tracker", \href{https://alice.cern/muon-forward-tracker}{https://alice.cern/muon-forward-tracker}
\bibitem{Ref:ALICE-detectors-MS}
ALICE Collaboration, ``Muon Spectrometer", \href{https://alice.cern/muon-spectrometer}{https://alice.cern/muon-spectrometer}
\bibitem{Ref:ALICE-detectors-ZDC}
ALICE Collaboration, ``Zero Degree Calorimeter", \href{https://alice.cern/zero-degree-calorimeters}{https://alice.cern/zero-degree-calorimeters}
\bibitem{Ref:O2-TDR}
Buncic, P and Krzewicki, M and Vande Vyvre, P, (2015), ``Technical Design Report for the Upgrade of the Online-Offline Computing System", \href{http://cds.cern.ch/record/2011297}{CERN-LHCC-2015-006, ALICE-TDR-019}.
\bibitem{Ref:jetQ-paper1}
C. Adler et al. (STAR Collaboration), 2003 Feb, ``Disappearance of back-to-back high-pT hadron correlations in central Au + Au collisions at $\sqrt{s_{NN}}$ = 200 GeV", \href{http://dx.doi.org/10.1103/PhysRevLett.90.082302}{Phys. Rev. Lett. \textbf{90}, 082302}.
\bibitem{Ref:jetQ-paper2}
J. Adams et al. (STAR Collaboration), 2003 Aug,``Evidence from d + Au measurements for final-state suppression of high-pT hadrons in Au + Au collisions at rhic”, \href{http://dx.doi.org/10.1103/PhysRevLett.91.072304}{Phys. Rev. Lett. \textbf{91}, 072304}.
\bibitem{Ref:flow-paper}
J. Adam et al. (ALICE Collaboration), 2016 02, ``Multiplicity and transverse momentum evolution of charge-dependent correlations in pp, p–pb, and pb–pb collisions at the lhc", The European Physical Journal C \textbf{76}
\bibitem{Ref:higgs-ATLAS}
The ATLAS Collaboration, ``Observation of a new particle in the search for the Standard Model Higgs boson with the ATLAS detector at the LHC", Physics Letters B. 716 (2012): 1–29. 2012. \href{https://arxiv.org/abs/1207.7214}{arXiv:1207.7214}
\bibitem{Ref:higgs-CMS}
``Observation of a new boson at a mass of 125 GeV with the CMS experiment at the LHC". Physics Letters B. \textbf{716} (2012): 30–61. 2012. \href{https://arxiv.org/abs/1207.7235}{arXiv:1207.7235}
\bibitem{Ref:CPviolation}
Mannel, Thomas (2–8 July 2006) \href{https://indico.cern.ch/event/427023/session/6/contribution/43/attachments/912026/1288208/Lancester-Mannel-Proc.pdf}{``Theory and phenomenology of CP violation" (PDF)}, The 7th International Conference on Hyperons, Charm and Beauty Hadrons (BEACH 2006), Nuclear Physics B. Vol. \textbf{167}, Lancaster: Elsevier. pp. 170–174.
\bibitem{Ref:neutrino-oscill}
B. Pontecorvo (May 1968). ``Neutrino Experiments and the Problem of Conservation of Leptonic Charge". \href{http://www.jetp.ac.ru/cgi-bin/e/index/e/26/5/p984?a=list}{Sov. Phys. JETP. 26: 984–988}.
\bibitem{Ref:matter-antimatter-prob}
``The matter-antimatter asymmetry problem", \href{https://home.cern/science/physics/matter-antimatter-asymmetry-problem}{https://home.cern/science/physics/matter-antimatter-asymmetry-problem}
\bibitem{Ref:dark-matter-y-energy}
Womersley, J. (February 2005), \href{https://web.archive.org/web/20071017160238/http://www.symmetrymagazine.org/pdfs/200502/beyond_the_standard_model.pdf}{"Beyond the Standard Model" (PDF)}, Symmetry Magazine. Archived from the original (unavailable) on 2007-10-17.
\bibitem{Ref:quarkpaper1}
 E. D. Bloom; et al, (1969), ``High-Energy Inelastic e–p Scattering at 6° and 10°", \href{https://doi.org/10.1103%2FPhysRevLett.23.930}{Physical Review Letters. 23 (16): 930–934}.
 \bibitem{Ref:quarkpaper2}
 M. Breidenbach; et al, (1969), ``Observed Behavior of Highly Inelastic Electron–Proton Scattering", \href{https://doi.org/10.1103%2FPhysRevLett.23.935}{Physical Review Letters. 23 (16): 935–939}.
 \bibitem{Ref:QGP-discovery}
 Heinz, Ulrich; Jacob, Maurice (2000-02-16), ``Evidence for a New State of Matter: An Assessment of the Results from the CERN Lead Beam Programme", \href{https://arxiv.org/abs/nucl-th/0002042}{arXiv:nucl-th/0002042}
 \bibitem{Ref:Csernai}
 László P. Csernai, \href{http://www.csernai.no/Csernai-textbook.pdf}{``Introduction to Relativistic Heavy Ion Collisions"}
 \bibitem{Ref:Hagedorn}
 Gaździcki, Marek; Gorenstein, Mark I, (2016), Rafelski, Johann (ed.), ``Hagedorn's Hadron Mass Spectrum and the Onset of Deconfinement", Melting Hadrons, Boiling Quarks – From Hagedorn Temperature to Ultra-Relativistic Heavy-Ion Collisions at CERN, Springer International Publishing, pp. 87–92, \href{https://arxiv.org/abs/1502.07684}{arXiv:1502.07684}
 \bibitem{Ref:jetQ-paper3}
 D. d’Enterria and B. Betz, 2009 11, ``High-pt hadron suppression and jet quenching”, ISBN 978-3-642-02285-2, pp. 285–339.
 \bibitem{Ref:etadep-paper1}
 L. Foà, 1975, ``Inclusive study of high-energy multiparticle production and two-body correlations”, \href{http://dx.doi.org/https://doi.org/10.1016/0370-1573(75)90050-2}{Physics Reports 22, 1–56}.
 \bibitem{Ref:etadep-paper2}
 J. Whitmore, 1976, ``Multiparticle production in the fermilab bubble chambers”, \href{http://dx.doi.org/https://doi.org/10.1016/0370-1573(76)90004-1}{Physics Reports 27, 187–273}.
 \bibitem{Ref:deta-paper}
 C. Pruneau, 2017, Data analysis techniques for physical scientists (Cambridge University Press).
\end{thebibliography}


author, papername, journalname(linked), year